\vspace{\baselineskip} The population of long-period transiting exoplanets \vspace{-2.5\baselineskip}

### 2016-07-20 document/ms.tex
some typos

The \kepler\ Mission has discovered thousands of exoplanets and revolutionized
our understanding of their population.
This large, homogeneous catalog of discoveries has enabled rigorous studies of
the occurrence rate of exoplanets and planetary systems as a function of their
physical properties.
However, transit surveys like \kepler\ are most sensitive to planets with
orbital periods shorter than a few years, which is shorter than the orbital periods of
Jupiter and Saturn, which dominate the dynamics of our Solar System.  To address this deficiency,
we performed a fully automated search for long-period exoplanets with only one
or two transits in the archival \kepler\ light curves.
When applied to the $\sim 40,000$ brightest Sun-like target stars, this search
produced \numcands\ long-period exoplanet candidates.
Of these candidates, 6 are novel discoveries and 5 are in systems with inner
short-period transiting planets.
Since our method involves no human intervention, we empirically characterize
the detection efficiency of our search.
Based on these results, we measure the average occurrence rate of exoplanets
smaller than Jupiter with orbital periods longer than two years to be $1.80\pm
0.65$ planets per Sun-like star.

@@

\dfmfig{model-comp} shows representative events that fall into different
classes and the corresponding maximum-likelihood model.
For each candidate event, the BIC of each of these models is computed and the
event is only passed as a candidate if the \modelname{transit} model is
preferred to all the other models.
The \modelname{box} model is the most restrictive comparison, vetoing about
half of the candidate events in the \kepler\ light curves, followed by the
\modelname{variability} model.
To further restrict to non-grazing transits, we also reject events where the
maximum impact parameter is greater than $1 - R_\mathrm{P} / R_\star$.

>>>>

The \kepler\ Mission has discovered thousands of exoplanets and revolutionized
our understanding of their population.
This large, homogeneous catalog of discoveries has enabled rigorous studies of
the occurrence rate of exoplanets and planetary systems as a function of their
physical properties.
However, transit surveys like \kepler\ are most sensitive to planets with
orbital periods shorter than a few years, which is shorter than the orbital periods of
Jupiter and Saturn, which dominate the dynamics of our Solar System.
To address this deficiency, we perform a fully automated search for
long-period exoplanets with only one or two transits in the archival \kepler\
light curves.
When applied to the $\sim 40,000$ brightest Sun-like target stars, this search
produces \numcands\ long-period exoplanet candidates.
Of these candidates, 6 are novel discoveries and 5 are in systems with inner
short-period transiting planets.
Since our method involves no human intervention, we empirically characterize
the detection efficiency of our search.
Based on these results, we measure the average occurrence rate of exoplanets
smaller than Jupiter with orbital periods longer than two years to be $1.80\pm
0.65$ planets per Sun-like star.

@@

\dfmfig{model-comp} shows representative events that fall into different
classes and the corresponding maximum likelihood model.
For each candidate event, the BIC of each of these models is computed and the
event is only passed as a candidate if the \modelname{transit} model is
preferred to all the other models.
The \modelname{box} model is the most restrictive comparison, vetoing about
half of the candidate events in the \kepler\ light curves, followed by the
\modelname{variability} model.
To further restrict to non-grazing transits, we also reject events where the
maximum likelihood impact parameter is greater than $1 - R_\mathrm{P} /
R_\star$.
